Appendix

### 2025-04-03 manuscript_rmarkdown/manuscript.Rmd
Switch central portion to 80%

Figure \ref{empirical-central-normality-kappa} shows $\tau_{\alpha = 0.95, n, \kappa}$
as a function of $n$ for different values of $\kappa$. With decreasing
$\kappa$, the test statistic curve decreases. The curves
for $\kappa = 0.60$ and $\kappa = 0.70$ are similar, whereas curves for 
$\kappa \geq 0.90$ are affected by outliers, as can be observed by comparing curves
of the central normality test with those of the empirical variant.

Since the (empirical) central normality tests assesses whether the central part of a sequence is normally distributed,
we used $\kappa = 0.70$. Lookup tables and curves for critical statistic values for central normality and empirical central
normality tests are shown in Appendix E.

@@

```{r empirical-central-normality-error_rate, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2.5}
cap <- paste0(
  "Observed type I error rates for (central) normality tests in the presence of data derived from normal distributions with and without outliers. ",
  "ECN: empirical central normality; CN: central normality"
)

@@

To find the optimal values for the weighting function parameters $\delta_1$ and $\delta_2$ (if applicable),
we minimised $\sum_{i=1}^{m_d = 100}\tau_{n_i, \kappa = 0.70, i}$, i.e. the mean of residual 
errors of the central 70% of elements of each sequence $\mathbf{X}_i$, summed over all sequences.

>>>>

Figure \ref{empirical-central-normality-kappa} shows $\tau_{\alpha = 0.95, n, \kappa}$
as a function of $n$ for different values of $\kappa$. With decreasing
$\kappa$, the test statistic curve decreases. The curves
for $\kappa = 0.60$, $\kappa = 0.70$ and $\kappa = 0.80$ are similar, whereas curves for 
$\kappa \geq 0.90$ are affected by outliers, as can be observed by comparing curves
of the central normality test with those of the empirical variant.

Since the (empirical) central normality tests assesses whether the central part of a sequence is normally distributed,
we used $\kappa = 0.80$. Lookup tables and curves for critical statistic values for central normality and empirical central
normality tests are shown in Appendix E.

@@

```{r empirical-central-normality-error_rate, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2.5}
cap <- paste0(
  "Observed type I error rates for (central) normality tests in the presence of data derived from normal distributions with and without outliers. ",
  "The empirical central normality (ECN) test uses $\\kappa = 0.80$. CN: central normality"
)

@@

To find the optimal values for the weighting function parameters $\delta_1$ and $\delta_2$ (if applicable),
we minimised $\sum_{i=1}^{m_d = 100}\tau_{n_i, \kappa = 0.80, i}$, i.e. the mean of residual 
errors of the central 80% of elements of each sequence $\mathbf{X}_i$, summed over all sequences.

### 2025-04-03 manuscript_rmarkdown/manuscript_appendix.Rmd
Switch central portion to 80%

central_normality_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = FALSE
)

empirical_central_normality_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = FALSE,
  with_outliers = TRUE
)

@@

```{r include = FALSE, eval = FALSE}
# This generates the table shown below.
.get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.70,
  for_manuscript = TRUE
)

@@

data <- .assess_standardisation_before_transformation()
data <- data[, mget(c("residuals", "lambda", "p_value", "transformation", "dataset"))]
data[, "residuals" := round(residuals, digits = 1L)]
data[, "lambda" := round(lambda, digits = 1L)]
data[, "p_value" := round(p_value, digits = 3L)]
data.table::dcast(data, transformation ~ dataset, value.var = "residuals")
data.table::dcast(data, transformation ~ dataset, value.var = "lambda")
data.table::dcast(data, transformation ~ dataset, value.var = "p_value")
```

>>>>

central_normality_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.80,
  for_manuscript = FALSE
)

empirical_central_normality_lookup_table <- .get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.80,
  for_manuscript = FALSE,
  with_outliers = TRUE
)

@@

```{r include = FALSE, eval = FALSE}
# This generates the table shown below.
.get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.80,
  for_manuscript = TRUE
)

@@

data <- .assess_standardisation_before_transformation()
data <- data[, mget(c("residuals_central", "lambda", "p_value", "transformation", "dataset"))]
data[, "residuals_central" := round(residuals_central, digits = 1L)]
data[, "lambda" := round(lambda, digits = 1L)]
data[, "p_value" := round(p_value, digits = 3L)]
data.table::dcast(data, transformation ~ dataset, value.var = "residuals_central")
data.table::dcast(data, transformation ~ dataset, value.var = "lambda")
data.table::dcast(data, transformation ~ dataset, value.var = "p_value")
```
